AA: The Algorithmic Autoregulation (Distributed Software Development) Methodology

### 2013-08-07 paper.tex
revisao feita, listada em https://etherpad.mozilla.org/paaper. parece ok para enviar a revista

The team members had different levels of experience on software development for
large and distributed free software projects like Scilab or Mozilla. In this
way, one month of training was conducted by three experienced developers (the
first authors of the present work), teaching
the basics of use of development infrastructure tools like bugtrackers, programming
languages, version control systems, and build systems. After this period, a
starter project was proposed for new developers: to submit a bugfix or implement
a new feature and have an accepted
patch or commit to the official repository for a large free
software project.  Developers passing the starter project would be deemed
`initiated' and be called a `Macambira' developer, and be hired for the
remainder of the semester.
Table~\ref{tabela:contribuicoes} summarizes the effective accepted contributions
of each successfully initiated developer to free software projects in 2011,
which used the AA methodology.

@@

As of this writing, `Lab Macambira' unites over 15 software developers, and 
key developers trained in 2011 continue to work voluntarily in the project.

>>>>

The team members had different levels of experience on software development for
large and distributed free software projects like Scilab or Mozilla. In this
way, one month of training was conducted by three experienced developers (the
first authors of the present work), teaching
the basics of use of development infrastructure tools like bugtrackers, programming
languages, version control systems, and build systems. After this period, a
starter project was proposed for new developers: to submit a bugfix or implement
a new feature and have an accepted
patch or commit to the official repository for a large free
software project.  Developers passing the starter project would be deemed
`initiated' and be called a `Macambira' developer, and be hired for the
remainder of the semester.
To illustrate the coverage of overall contributions by `Macambira' developers, Table~\ref{tabela:contribuicoes} summarizes the effective accepted commits
of each successfully initiated developer to free software projects in 2011,
which used the AA methodology.

@@

As of this writing, `Lab Macambira' unites over 15 software developers, and 
key developers trained in 2011 continue to work voluntarily in the project and
as voluntaries and contracted developers on fundations like Mozilla.
